Detecting ditches using supervised learning on high-resolution digital elevation models

### 2021-01-24 LaTeX ESWA/version-21-01-17.tex
Makes some adjustments to article after meeting. Adds article highlights.

\begin{flushleft}
\small  
$^a$ J\"onk\"oping Artificial Intelligence Laboratory, J\"onk\"oping University, Gjuterigatan 5, 551 11, J\"onk\"oping, Sweden \\
$^b$ Forest Department, Swedish Forest Agency, Skeppargatan 17, 931 32 Skellefte\aa, Sweden \\
$^c$ Department of Forest Ecology and Management, Swedish University of Agricultural Sciences, SLU, Skogsmarksgr\"and 17, 901 83, Ume\aa, Sweden

@@

\vspace{1cm}
\textbf{Corresponding Author:} \\
Niklas Lavesson \\
J\"onk\"oping Artificial Intelligence Laboratory, J\"onk\"oping University, Gjuterigatan 5, 551 11, J\"onk\"oping, Sweden \\
Tel: (+46) 70-5383338 \hl{Ska detta nummer st\aa  h\"ar? (corresponding author m\aa ste ha telefonnummer)} \\
Email: niklas.lavesson@ju.se

@@

\cortext[cor1]{Corresponding author.}
\address[ju]{J\"onk\"oping Artificial Intelligence Laboratory, J\"onk\"oping University, Gjuterigatan 5, 551 11, J\"onk\"oping, Sweden}
\address[fa]{Forest Department, Swedish Forest Agency, Skeppargatan 17, 931 32 Skellefte\aa, Sweden}
\address[slu]{Department of Forest Ecology and Management, Swedish University of Agricultural Sciences, SLU, Skogsmarksgr\"and 17, 901 83, Ume\aa, Sweden}
\cortext[equal_contribution]{Jonatan Flyckt and Filip Andersson contributed equally to this work as first authors.}

>>>>

\begin{flushleft}
\small  
$^a$ Department of Computer Science, School of Engineering, J\"onk\"oping University, Gjuterigatan 5, 553 18, J\"onk\"oping, Sweden \\
$^b$ Forest Department, Swedish Forest Agency, Skeppargatan 17, 931 32 Skellefte\aa, Sweden \\
$^c$ Department of Forest Ecology and Management, Swedish University of Agricultural Sciences, SLU, Skogsmarksgr\"and 17, 901 83, Ume\aa, Sweden

@@

\vspace{1cm}
\textbf{Corresponding Author:} \\
Niklas Lavesson \\
Department of Computer Science\newline School of Engineering, J\"onk\"oping University \newline Gjuterigatan 5, 553 18, J\"onk\"oping, Sweden \\
Tel: (+46) 70-5383338 \\
Email: niklas.lavesson@ju.se

@@

\cortext[cor1]{Corresponding author.}
\address[ju]{Department of Computer Science, School of Engineering, J\"onk\"oping University, Gjuterigatan 5, 553 18, J\"onk\"oping, Sweden}
\address[fa]{Forest Department, Swedish Forest Agency, Skeppargatan 17, 931 32 Skellefte\aa, Sweden}
\address[slu]{Department of Forest Ecology and Management, Swedish University of Agricultural Sciences, SLU, Skogsmarksgr\"and 17, 901 83, Ume\aa, Sweden}
\cortext[equal_contribution]{Jonatan Flyckt and Filip Andersson contributed equally to this work as first authors.}
